Algorithms for the Automated Correction of Vertical Drift in Eye Tracking Data

### 2020-10-19 manuscript/manuscript.tex
Added acknowledgement of the reviewers
Added NEWMATERIAL command
Unify submission and preprint versions

@@

%%%%%%%%%%%%%%%%%%%%% PREPRINT VERSION %%%%%%%%%%%%%%%%%%%%%

@@

%%%%%%%%%%%%%%%%%%%% SUBMISSION VERSION %%%%%%%%%%%%%%%%%%%%

% \fiveauthors{Jon W. Carr}{Valentina N. Pescuma}{Michele Furlan}{Maria Ktori}{Davide Crepaldi}

% \fiveaffiliations{Cognitive Neuroscience, International School for Advanced Studies (SISSA)\\Via Bonomea 265, 34136 Trieste TS, Italy\\+39 338 360 3224, jcarr@sissa.it}{Cognitive Neuroscience, International School for Advanced Studies (SISSA)}{Cognitive Neuroscience, International School for Advanced Studies (SISSA)}{Cognitive Neuroscience, International School for Advanced Studies (SISSA)}{Cognitive Neuroscience, International School for Advanced Studies (SISSA)}

% \authornote{This work was funded by an ERC Starting Grant (no.\@ 679010, STATLEARN) and a FARE 2016 grant (no.\@ R164XBHNYR, CROWDLEARN), both awarded to \textbf{DC}. \textbf{VNP}, \textbf{MK}, and \textbf{DC} conceived the original idea behind this work. \textbf{JWC} and \textbf{VNP} explored the literature and selected the algorithms. \textbf{VNP} and \textbf{MF} developed the \texttt{split} algorithm, with input from \textbf{MK} and \textbf{DC}. \textbf{JWC} developed the \texttt{warp} algorithm, implemented all algorithms in a single framework, conducted the simulations, and performed the analyses. \textbf{JWC} and \textbf{VNP} performed the manual corrections and drafted the paper. \textbf{DC} revised the paper and coordinated the project.}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

%%%%%%%%%%%%%%%%%%%%% PREPRINT VERSION %%%%%%%%%%%%%%%%%%%%%

\section{Acknowledgments}

This work was funded by an ERC Starting Grant (no.\@ 679010, STATLEARN) and a FARE 2016 grant (no.\@ R164XBHNYR, CROWDLEARN), both awarded to \textbf{DC}. \textbf{VNP}, \textbf{MK}, and \textbf{DC} conceived the original idea behind this work. \textbf{JWC} and \textbf{VNP} explored the literature and selected the algorithms. \textbf{VNP} and \textbf{MF} developed the \texttt{split} algorithm, with input from \textbf{MK} and \textbf{DC}. \textbf{JWC} developed the \texttt{warp} algorithm, implemented all algorithms in a single framework, conducted the simulations, and performed the analyses. \textbf{JWC} and \textbf{VNP} performed the manual corrections and drafted the paper. \textbf{DC} revised the paper and coordinated the project.

%%%%%%%%%%%%%%%%%%%% SUBMISSION VERSION %%%%%%%%%%%%%%%%%%%%

% \section{Open Practices Statement}

% All code and data required to reproduce the analyses reported in this paper, as well as Matlab/Octave, Python, and R implementations of the algorithms, are available from the OSF archive associated with this paper: https://doi.org/10.17605/OSF.IO/7SRKG Preregistration is not applicable to this study.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

>>>>

% HIGHLIGHTING OF NEW MATERIAL
\usepackage{xcolor}
\newcommand\NEWMATERIAL[1]{\textcolor{blue}{#1}}
% HIGHLIGHTING OF NEW MATERIAL

@@

@@

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Acknowledgments}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

The authors are grateful to the editor, Victor Kuperman, and reviewers, Sascha Schroeder and Tim Slattery, for helpful and insightful commentary. This work was funded by an ERC Starting Grant (no.\@ 679010, STATLEARN) and a FARE 2016 grant (no.\@ R164XBHNYR, CROWDLEARN), both awarded to \textbf{DC}. \textbf{VNP}, \textbf{MK}, and \textbf{DC} conceived the original idea behind this work. \textbf{JWC} and \textbf{VNP} explored the literature and selected the algorithms. \textbf{VNP} and \textbf{MF} developed the \texttt{split} algorithm, with input from \textbf{MK} and \textbf{DC}. \textbf{JWC} developed the \texttt{warp} algorithm, implemented all algorithms in a single framework, conducted the simulations, and performed the analyses. \textbf{JWC} and \textbf{VNP} performed the manual corrections and drafted the paper. \textbf{DC} revised the paper and coordinated the project.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Open Practices Statement}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

All code and data required to reproduce the analyses reported in this paper, as well as Matlab/Octave, Python, and R implementations of the algorithms, are available from the OSF archive associated with this paper: https://doi.org/10.17605/OSF.IO/7SRKG
